### 2014-06-28 tex/pseudo-code.tex
Added global invariant to machine state, and changed the References-Equals rules to reflect it's use
Fixed a typo that was causing an error in psuedo-code.tex
Almost done with lazy initialization

\begin{comment}
 defined on value sets $L$ and references
$R$. $R$ and $L$ include the special symbol $\bot$ to indicate an
uninitialized reference and location respectively. Additionally, $L$
includes a special location $\mathtt{NULL}$ for null references.
\end{comment}

@@

The function $\mathbb{VS}(L,R,r,f)$ constructs the value-set given a
heap, reference, and desired field such that
$(l^\prime\ \phi^\prime\wedge\phi) \in \mathbb{VS}(L,R,r,f)$ if and
only if
\[
\begin{array}{l}
  \exists (l\ \phi) \in L(r) ( \\
  \ \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
  \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists (l^\prime\ \phi^\prime) \in L(r^\prime) (\mathbb{S}(\phi\wedge\phi^\prime))))
\end{array}
\]
where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.

The function $\mathbb{CP}(L,r,\phi^\prime)$ constructs the location, constraint
pair $(l\ \phi\wedge\phi^\prime)$ such that $(l\ \phi\wedge\phi^\prime)\in\mathbb{CP}(L,r,\phi^\prime)$ if and only if $\exists (l\ \phi)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime)$

>>>>

@@

The function $\mathbb{VS}(L,R,\phi_g,r,f)$ constructs the value-set given a
heap, reference, and desired field:
\[
\begin{array}{rcl}
  \mathbb{VS}(L,R,\phi_g,r,f) & = & \{(l^\prime\ \phi^\prime\wedge\phi) \mid \\
  & & \ \ \ \ \exists l\ ((l\ \phi) \in L(r)\ \wedge \\
  & & \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
  & & \ \ \ \ \ \ \ \ \ \ \ \ (l^\prime\ \phi^\prime) \in L(r^\prime)\ \wedge\\
  & & \ \ \ \ \ \ \ \ \ \ \ \ \mathbb{S}(\phi\wedge\phi^\prime\wedge \phi_g)))\}
\end{array}
\]
where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.

The strengthen function $\mathbb{ST}(L,r,\phi^\prime)$ strengthens every
constraint from the reference $r$ with $\phi^\prime$ and keeps only location-constraint
pairs that are satisfiable after this strengthening:
\[
\begin{array}{rcl} 
\mathbb{ST}(L,r,\phi^\prime) & = & \{ (l\ \phi\wedge\phi^\prime) \mid 
(l\ \phi)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime) \}
\end{array}
\]
